Basque-Spanish Apertium translation system evaluation

### 2015-02-10 2015-eamt-assim/eng-kaz/tables-updated.tex
move dir
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58814 72bbbca6-d526-0410-a7d9-f06f51895060

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
%\date{}							% Activate to display a given date or no date
\usepackage{float}
\restylefloat{table}

\begin{document}
\section{General results}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&40.34 +/- 39.19&49.03 +/- 43.06&58.15 +/- 42.62&48.13 +/- 42.77\\
20\%&37.72 +/- 32.24&43.46 +/- 32.07&56.88 +/- 33.36&59.99 +/- 29.47\\
30\%&33.73 +/- 28.74&37.03 +/- 27.98&54.25 +/- 26.09&52.95 +/- 25.64\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&42.68&51.27&63.03&48.50\\
20\%&38.71&46.24&58.18&62.00\\
30\%&36.67&36.70&51.04&55.27\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&45.96 +/- 40.86&53.52 +/- 43.57&63.76 +/- 41.15&57.02 +/- 41.57\\
20\%&38.56 +/- 32.11&45.60 +/- 31.23&59.77 +/- 33.10&64.93 +/- 30.95\\
30\%&35.45 +/- 29.76&40.00 +/- 28.16&55.83 +/- 26.13&58.77 +/- 28.07\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&46.34&54.43&66.06&53.89\\
20\%&39.43&48.39&60.73&65.33\\
30\%&38.39&39.66&52.59&59.90\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&1:44 +/- 7:18&0:50 +/- 1:05&1:14 +/- 1:52&1:26 +/- 1:10\\
20\%&0:57 +/- 1:22&1:19 +/- 2:34&1:39 +/- 3:02&3:26 +/- 8:44\\
30\%&1:20 +/- 1:50&1:14 +/- 1:12&2:05 +/- 6:36&2:36 +/- 6:26\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&272\\
20\%&396\\
30\%&724\\
\hline
\end{tabular}
\caption {Total number of holes to be filled} \label{tab:title}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&0.517 &0.711 &0.459 &0.598\\
20\%&0.261 &0.473 &0.667 &0.740\\
30\%&0.412 &0.411 &0.581 &0.534\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}

\section{Results by topic}
\subsection{Casual conversations}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&46.97 +/- 44.28&53.03 +/- 47.58&48.48 +/- 45.20&51.52 +/- 46.85\\
20\%&35.56 +/- 31.18&37.22 +/- 29.17&59.44 +/- 35.92&63.89 +/- 29.21\\
30\%&33.54 +/- 31.47&34.58 +/- 27.22&56.11 +/- 23.82&59.17 +/- 28.05\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&50.00&57.50&48.78&50.00\\
20\%&35.44&39.24&59.21&65.79\\
30\%&37.63&37.50&53.85&59.09\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&53.03 +/- 44.28&62.12 +/- 46.11&63.64 +/- 43.12&63.64 +/- 44.84\\
20\%&37.78 +/- 30.94&41.11 +/- 27.88&63.33 +/- 35.85&73.33 +/- 31.51\\
30\%&37.71 +/- 33.32&39.44 +/- 27.10&59.58 +/- 23.89&70.28 +/- 31.12\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&54.76&65.00&60.98&59.52\\
20\%&37.97&44.30&63.16&73.68\\
30\%&41.94&41.67&58.24&68.18\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&3:35 +/- 11:43&0:45 +/- 1:00&1:03 +/- 1:14&1:28 +/- 1:16\\
20\%&0:33 +/- 0:31&0:47 +/- 0:41&0:38 +/- 0:36&0:52 +/- 1:28\\
30\%&1:09 +/- 2:21&0:49 +/- 0:42&0:40 +/- 0:29&0:53 +/- 0:54\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&60\\
20\%&124\\
30\%&184\\
\hline
\end{tabular}
\caption {Total number of holes to be filled} \label{tab:title}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&0.411 &0.601 &0.426 &0.504\\
20\%&0.235 &0.371 &0.570 &0.712\\
30\%&0.121 &0.459 &0.846 &0.310\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}

\subsection{Legal texts}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&29.10 +/- 29.64&38.77 +/- 37.82&68.21 +/- 34.99&53.02 +/- 40.31\\
20\%&48.31 +/- 33.52&50.28 +/- 33.55&65.76 +/- 24.16&60.57 +/- 24.98\\
30\%&33.68 +/- 28.16&38.49 +/- 27.81&48.30 +/- 28.87&47.39 +/- 26.29\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&35.21&43.48&67.11&52.00\\
20\%&43.31&52.46&63.57&61.74\\
30\%&36.17&35.16&41.32&53.76\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&32.95 +/- 34.88&38.77 +/- 37.82&68.21 +/- 34.99&53.02 +/- 40.31\\
20\%&48.31 +/- 33.52&50.28 +/- 33.55&65.76 +/- 24.16&60.57 +/- 24.98\\
30\%&34.15 +/- 28.73&40.05 +/- 27.37&48.30 +/- 28.87&50.06 +/- 26.25\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&38.03&43.48&67.11&52.00\\
20\%&43.31&52.46&63.57&61.74\\
30\%&37.23&37.36&41.32&56.07\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&0:49 +/- 1:13&1:04 +/- 1:21&1:17 +/- 1:01&1:34 +/- 1:03\\
20\%&1:32 +/- 2:02&2:28 +/- 4:18&3:26 +/- 4:41&8:22 +/- 13:46\\
30\%&1:13 +/- 1:36&1:19 +/- 1:21&3:32 +/- 10:24&2:57 +/- 4:00\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&132\\
20\%&244\\
30\%&284\\
\hline
\end{tabular}
\caption {Total number of holes to be filled} \label{tab:title}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&0.543 &0.481 &0.402 &0.642\\
20\%&0.317 &0.453 &0.631 &0.652\\
30\%&0.488 &0.301 &0.426 &0.532\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}

\subsection{News}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&42.78 +/- 38.41&54.02 +/- 40.51&59.77 +/- 43.66&40.00 +/- 38.87\\
20\%&28.97 +/- 28.79&44.44 +/- 32.51&43.70 +/- 34.86&54.46 +/- 33.34\\
30\%&33.98 +/- 26.52&37.65 +/- 28.77&59.83 +/- 22.90&53.70 +/- 20.22\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&47.06&57.14&68.75&42.00\\
20\%&34.25&43.59&47.14&58.67\\
30\%&36.72&38.28&61.72&54.69\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&49.44 +/- 39.08&57.47 +/- 42.12&59.77 +/- 43.66&53.33 +/- 37.86\\
20\%&28.97 +/- 28.79&46.53 +/- 31.99&48.56 +/- 35.40&59.33 +/- 33.89\\
30\%&34.81 +/- 27.01&40.51 +/- 30.10&61.49 +/- 22.11&58.14 +/- 22.42\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&50.98&61.22&68.75&52.00\\
20\%&34.25&46.15&52.86&64.00\\
30\%&37.50&41.41&63.28&59.38\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, average} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT and source hint\\
\hline
10\%&0:31 +/- 0:20&0:42 +/- 0:49&1:25 +/- 2:49&1:17 +/- 1:09\\
20\%&0:50 +/- 0:53&0:49 +/- 0:42&0:56 +/- 0:39&1:05 +/- 0:33\\
30\%&1:38 +/- 1:28&1:31 +/- 1:17&1:40 +/- 1:12&3:53 +/- 10:27\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence} \label{tab:title} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&80\\
20\%&148\\
30\%&256\\
\hline
\end{tabular}
\caption {Total number of holes to be filled} \label{tab:title}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&0.537 &0.917 &0.574 &0.598\\
20\%&0.143 &0.644 &0.850 &0.928\\
30\%&0.513 &0.456 &0.532 &0.644\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}

>>>>

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%\date{}							% Activate to display a given date or no date

\begin{document}
%\section{}
%\subsection{}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&40.48 +/- 45.30&30.16 +/- 35.86&38.10 +/- 46.05&35.33 +/- 38.68\\
20\%&54.63 +/- 27.53&39.19 +/- 20.37&24.79 +/- 19.16&48.78 +/- 32.65\\
30\%&23.87 +/- 24.95&35.13 +/- 30.18&30.41 +/- 34.73&43.07 +/- 32.71\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&31.43&27.50&34.15&30.43\\
20\%&51.72&36.23&22.54&43.84\\
30\%&21.85&32.58&25.56&35.63\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, average} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&40.48 +/- 45.30&42.06 +/- 38.70&42.86 +/- 44.42&39.33 +/- 37.38\\
20\%&63.89 +/- 28.87&49.78 +/- 19.89&36.01 +/- 24.61&48.78 +/- 32.65\\
30\%&32.08 +/- 27.38&49.42 +/- 25.61&45.01 +/- 37.62&47.04 +/- 33.64\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&31.43&40.00&39.02&34.78\\
20\%&60.34&47.83&33.80&43.84\\
30\%&31.09&44.94&36.56&41.38\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, average} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&0:47 +/- 0:35&1:47 +/- 1:36&1:34 +/- 1:03&3:18 +/- 2:35\\
20\%&1:13 +/- 1:02&2:24 +/- 2:21&2:19 +/- 2:07&1:31 +/- 1:21\\
30\%&4:20 +/- 11:28&2:01 +/- 1:49&3:21 +/- 4:18&2:00 +/- 1:30\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence (m:s)} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&22\\
20\%&43\\
30\%&52\\
\hline
\end{tabular}
\caption {Total number of holes to be filled by one evaluator.} \label{tab:title}
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & No hint & Source hint & MT hint & MT ans Source hint\\
\hline
10\%&0.812&0.000&0.516&0.143\\
20\%&0.638&0.282&0.425&0.507\\
30\%&0.521&0.348&0.795&0.413\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}

### 2015-02-10 2015-eamt-assim/eu-es/tables.tex
move dir
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58814 72bbbca6-d526-0410-a7d9-f06f51895060

%\date{}							% Activate to display a given date or no date

\begin{document}
%\section{}
%\subsection{}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&35.33 +/- 38.68&38.10 +/- 46.05&40.48 +/- 45.30&30.16 +/- 35.86\\
20\%&48.78 +/- 32.65&24.79 +/- 19.16&54.63 +/- 27.53&39.19 +/- 20.37\\
30\%&43.07 +/- 32.71&30.41 +/- 34.73&23.87 +/- 24.95&35.13 +/- 30.18\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&30.43&34.15&31.43&27.50\\
20\%&43.84&22.54&51.72&36.23\\
30\%&35.63&25.56&21.85&32.58\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference, average} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&39.33 +/- 37.38&42.86 +/- 44.42&40.48 +/- 45.30&42.06 +/- 38.70\\
20\%&48.78 +/- 32.65&36.01 +/- 24.61&63.89 +/- 28.87&49.78 +/- 19.89\\
30\%&47.04 +/- 33.64&45.01 +/- 37.62&32.08 +/- 27.38&49.42 +/- 25.61\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, mean and standard deviation} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&34.78&39.02&31.43&40.00\\
20\%&43.84&33.80&60.34&47.83\\
30\%&41.38&36.56&31.09&44.94\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list, average} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&3:18 +/- 2:35&1:34 +/- 1:03&0:47 +/- 0:35&1:47 +/- 1:36\\
20\%&1:31 +/- 1:21&2:19 +/- 2:07&1:13 +/- 1:02&2:24 +/- 2:21\\
30\%&2:00 +/- 1:30&3:21 +/- 4:18&4:20 +/- 11:28&2:01 +/- 1:49\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence (m:s)} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&22\\
20\%&43\\
30\%&52\\
\hline
\end{tabular}
\caption {Total number of holes to be filled by one evaluator.} \label{tab:title}
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&0.143&0.516&0.812&0.000\\
20\%&0.507&0.425&0.638&0.282\\
30\%&0.413&0.795&0.521&0.348\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}

>>>>

\title{Basque-Spanish Apertium translation system evaluation}
\begin{document}
%\subsection{}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&47.90 +/- 35.16&58.04 +/- 27.96&34.65 +/- 37.69&33.84 +/- 36.86\\
20\%&46.30 +/- 25.14&52.73 +/- 23.73&26.52 +/- 27.64&30.16 +/- 28.46\\
30\%&38.71 +/- 22.71&28.89 +/- 19.54&16.26 +/- 17.35&20.92 +/- 18.75\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference.} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&62.19 +/- 32.07&58.04 +/- 27.96&48.79 +/- 39.84&39.90 +/- 38.96\\
20\%&64.81 +/- 30.03&70.18 +/- 26.98&30.91 +/- 30.22&31.37 +/- 28.42\\
30\%&48.13 +/- 26.08&39.55 +/- 23.90&18.07 +/- 18.15&25.94 +/- 19.67\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list.} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&49.38&55.70&35.06&32.47\\
20\%&48.23&55.64&30.14&32.31\\
30\%&41.64&29.97&17.67&20.14\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), exactly as in reference.} \label{tab:title}
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&58.02&55.70&45.45&35.06\\
20\%&65.96&68.42&33.56&33.85\\
30\%&49.84&37.28&18.93&24.23\\
\hline
\end{tabular}
\caption {Gaps successfully filled (\%), using a synonym list.} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{1}{c}|}
\hline
Gap percentage & Number of holes\\
\hline
10\%&94\\
20\%&181\\
30\%&272\\
\hline
\end{tabular}
\caption {Total number of holes to be filled.} \label{tab:title}
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&1:27 +/- 1:27&1:47 +/- 1:57&0:46 +/- 0:44&1:06 +/- 0:38\\
20\%&1:31 +/- 1:19&1:24 +/- 1:17&1:22 +/- 1:17&1:27 +/- 1:02\\
30\%&3:54 +/- 5:02&2:50 +/- 1:51&2:47 +/- 2:07&2:36 +/- 1:22\\
\hline
\end{tabular}
\caption {Time taken to fill the gaps in one sentence (m:s)} \label{tab:title} 
\end{table}

\begin{table}
\centering
\begin{tabular}{|r |*{4}{c}|}
\hline
 &\multicolumn{4}{c|}{Evaluation mode}\\
\hline
Gap percentage & MT and source hint & MT hint & No hint & Source hint\\
\hline
10\%&0.496&0.517&0.124&0.400\\
20\%&0.714&0.700&0.275&0.358\\
30\%&0.559&0.430&0.300&0.406\\
\hline
\end{tabular}
\caption {Krippendorff Alpha measure} \label{tab:title}
\end{table}
